---
title: "Markdown Practice"
author: "Josh Emerson"
date: "10 August 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


practice R markdown document, trying to outline this week's class

### Course Topics

#### Part I: Data Science Best Practices
1. Overview and Introduction
1. Workflow and RStudio
1. R Coding and Scripting Basics
1. Working with GIS
1. Version control using Git
1. Data Science Best Practices
1. Part I Wrap Up

#### Part II: tidyverse workflow
1. Overview of the tidyverse workflow
1. Data importing
1. Tidy data
1. Data manipulation with dplyr
1. Data visulization with ggplot2
1. Data modeling with Split-Apply-Combine
1. Producing Reports With R Markdown
1. Part II Wrap Up

### Load Packages
```{r eval = FALSE}
library(tidyverse)
library(lubridate)
library(broom)
require(readxl)
```

### Loading Data

```{r eval = FALSE} 
input_file <- "data/Hawthorne Tilikum Steel daily bike counts 073118.xlsx"
bridge_name <- "Hawthorne"}
```




### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
